Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-30 latex/comp_or.tex
Comp OR paper update

\begin{equation} \label{eq:costs}
	\tilde{c} = c_{0,\pi(1)}\times(1+c_g\times|\epsilon_0|) + \sum_{k=1}^{K-1} \Big [ c^{\pi(k), \pi(k+1)}\times(1+c_g\times|\epsilon^{\pi_k}|) \Big ] + c^{\pi(K),0}\times(1+c_g\times|\epsilon_K|)
\end{equation}

@@

		\State $\pi[0] \gets 0$ \label{tour:pi1}
		\State $\pi(K+1) \gets 0$ \label{tour:pi2}
		\State $score \gets 0$ \label{tour:score}
		\State $cost \gets 0$ \label{tour:cost}
		\For {$k\gets0$ to $K$} \label{tour:loop1}		
			\For{$i \gets 1$ to $m$}
				\State $p_i.to[k] \gets -1$ \label{tour:-1} \Comment{reset this pallet destination}
			\EndFor	
			\If {$k = 0$}
				\State $L_0 \gets L$
				\State Let $G_1(M \cup N_0, \varnothing)$ \label{tour:g11}
			\Else
				\State $L_k \gets L_k - \pi(k)$  \label{tour:lk1}			
				\State $Q^{\pi_k}, E_Q^{\pi_k}, M^{\pi_k} \gets UpdateConsolidated(\pi(k))$ \label{tour:dest}			
				\State Let $G_1(M^{\pi_k} \cup N^{\pi_k} \cup Q^{\pi_k}, E_Q^{\pi_k})$ \label{tour:g12}
			\EndIf  \label{tour:lk2}	
			\State $M^{\pi_k} \gets SetPalletsDestinations( \pi(k) )$ \label{tour:dest2}		
			\State $G_2 \gets SolveNode(method, \pi(k), G_1, timeLim)$ \label{tour:node}

@@

			\State $s, \epsilon \gets ScoreAndDeviation(\pi(k), G_4)$ \label{tour:analyse}
			\State $score \gets score + s$ \label{tour:score2}
			\State $cost \gets cost + c_{\pi(k),\pi(k+1)} * (1 + c_g * |\epsilon|)$ \label{tour:cost2} 
		\EndFor  \label{tour:loop2}
		\Return $score / cost$ \label{tour:f}

@@

$ScoreAndDeviation(\pi(k), G_4)$ evaluates the allocation graph generated by $SolveNode$, returning the corresponding score and CG deviation. It consists of a loop that goes through all the pallets, accumulating the scores and the torques of the shipped items, allowing the final calculation of the CG deviation.

@@

		\Procedure{$mpShims$}{${N^{\pi_k}, \pi(k)}, limit, G$}

@@

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets Greedy(p_i,\ N^{\pi_k},\ \pi(k),\ nodeTorque,\ G,\ limit,\ lock,\ ts )$   \label{mpShims:greedy}
		\State $proc_i.fork$
		\EndFor

@@

		\State $minCGdev(M^{\pi_k},\ \pi(k),\ nodeTorque)$  \label{mpShims:minCGdev} \Comment{minimize the CG deviation.}

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets getBestShims(p_i,\ N^{\pi_k},\ \pi(k),\ nodeTorque,\ G,\ surplus,\ lock,\ ts )$ \label{mpShims:getBestShims}
		\State $proc_i.fork$
		\EndFor

@@

		\Procedure{$getBestShims$}{$i,\ \eta_1,\ \eta_2,\ E,\ k,\ slack$}

@@

		\If { $e_{ij}^{\pi_k} \not\in (E_N^{\pi_k} \cup shims)$ {\bf and} $e_{ij}^{\pi_k}$ is feasible  {\bf and}  $(t_j^k.v + volume) \leq slack^i$}

		\State $shims \gets shims \cup \{e_{ij}^{\pi_k}\}$
		\State $volume \gets volume + t_j^k.v$
		\State $NewShims \gets$ {\bf False} \label{new_shims_false}

@@

		\State $sh_w \gets shims$, where $shims \in Set$ and $\sum_{e_{ab}^k \in shims} t_b^k.w$ is maximum  \label{best_weight}		
		\State $sh_v \gets shims$, where $shims \in Set$ and $\sum_{e_{ab}^k \in shims} t_b^k.v$ is maximum \label{best_volume}
		\State $sh_{best} \gets shims$, where $shims \in \{sh_w, sh_v\}$ and $\sum_{e_{ab}^k \in x} t_b^k.s$ is maximum \label{best_score}

@@

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets 3Dpacker(p_i,\ N^{\pi_k}_i,\ \pi(k),\ G )$   \label{3dpacking:3}
		\State $proc_i.fork$ \Comment{pallet $p_i$ packing processes is forked}
		\EndFor

@@

Equation \ref{eq:distobj} minimizes the sum of distances of the consolidated in node $\pi_k$ destined to the next node $\pi(k+1)$;

>>>>

\begin{equation} \label{eq:costs}
	\tilde{c} = c_{0,\pi(1)}\times(1+c_g\times|\epsilon_0|) + \sum_{k=1}^{K-1} \Big [ c^{\pi_k, \pi(k+1)}\times(1+c_g\times|\epsilon^{\pi_k}|) \Big ] + c^{\pi_k,0}\times(1+c_g\times|\epsilon_K|)
\end{equation}

@@

		\State $\pi_0 \gets 0$ \label{tour:pi1}
		\State $\pi_{K+1} \gets 0$ \label{tour:pi2}
		\State $score \gets 0$ \label{tour:score}
		\State $cost \gets 0$ \label{tour:cost}
		\For {$k\gets0$ to $K$} \label{tour:loop1}		
			\For{$i \gets 1$ to $m$}
				\State $p_i.to^{\pi_k} \gets -1$ \label{tour:-1} \Comment{reset this pallet destination}
			\EndFor	
			\If {$k = 0$}
				\State $L^{\pi_0} \gets L$
				\State Let $G_1(M \cup N_0, \varnothing)$ \label{tour:g11}
			\Else
				\State $L^{\pi_k} \gets L^{\pi_k} - \{\pi_k\}$  \label{tour:lk1}			
				\State $Q^{\pi_k}, E_Q^{\pi_k}, M^{\pi_k} \gets UpdateConsolidated(\pi_k)$ \label{tour:dest}			
				\State Let $G_1(M^{\pi_k} \cup N^{\pi_k} \cup Q^{\pi_k}, E_Q^{\pi_k})$ \label{tour:g12}
			\EndIf  \label{tour:lk2}	
			\State $M^{\pi_k} \gets SetPalletsDestinations( \pi_k )$ \label{tour:dest2}		
			\State $G_2 \gets SolveNode(method, \pi_k, G_1, timeLim)$ \label{tour:node}

@@

			\State $s, \epsilon \gets ScoreAndDeviation(\pi_k, G_4)$ \label{tour:analyse}
			\State $score \gets score + s$ \label{tour:score2}
			\State $cost \gets cost + c_{\pi_k, \pi_{k+1}} * (1 + c_g * |\epsilon|)$ \label{tour:cost2} 
		\EndFor  \label{tour:loop2}
		\Return $score / cost$ \label{tour:f}

@@

$ScoreAndDeviation(\pi_k, G_4)$ evaluates the allocation graph generated by $SolveNode$, returning the corresponding score and CG deviation. It consists of a loop that goes through all the pallets, accumulating the scores and the torques of the shipped items, allowing the final calculation of the CG deviation.

@@

		\Procedure{$mpShims$}{${N^{\pi_k}, \pi_k}, limit, G$}

@@

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets Greedy(p_i,\ N^{\pi_k},\ \pi_k,\ nodeTorque,\ G,\ limit,\ lock,\ ts )$   \label{mpShims:greedy}
		\State $proc_i.fork$
		\EndFor

@@

		\State $minCGdev(M^{\pi_k},\ \pi_k,\ nodeTorque)$  \label{mpShims:minCGdev} \Comment{minimize the CG deviation.}

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets getBestShims(p_i,\ N^{\pi_k},\ \pi_k,\ nodeTorque,\ G,\ surplus,\ lock,\ ts )$ \label{mpShims:getBestShims}
		\State $proc_i.fork$
		\EndFor

@@

		\Procedure{$getBestShims$}{$i,\ \eta_1,\ \eta_2,\ E,\ \pi_k,\ slack$}

@@

		\If { $e_{ij}^{\pi_k} \not\in (E_N^{\pi_k} \cup shims)$ {\bf and} $e_{ij}^{\pi_k}$ is feasible  {\bf and}  $(t_j^{\pi_k}.v + volume) \leq slack^i$}

		\State $shims \gets shims \cup \{e_{ij}^{\pi_k}\}$
		\State $volume \gets volume + t_j^{\pi_k}.v$
		\State $NewShims \gets$ {\bf False} \label{new_shims_false}

@@

		\State $sh_w \gets shims$, where $shims \in Set$ and $\sum_{e_{ab}^{\pi_k} \in shims} t_b^{\pi_k}.w$ is maximum  \label{best_weight}		
		\State $sh_v \gets shims$, where $shims \in Set$ and $\sum_{e_{ab}^{\pi_k} \in shims} t_b^{\pi_k}.v$ is maximum \label{best_volume}
		\State $sh_{best} \gets shims$, where $shims \in \{sh_w, sh_v\}$ and $\sum_{e_{ab}^{\pi_k} \in x} t_b^{\pi_k}.s$ is maximum \label{best_score}

@@

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets 3Dpacker(p_i,\ N^{\pi_k}_i,\ \pi_k,\ G )$   \label{3dpacking:3}
		\State $proc_i.fork$ \Comment{pallet $p_i$ packing processes is forked}
		\EndFor

@@

Equation \ref{eq:distobj} minimizes the sum of distances of the consolidated in node $\pi_k$ destined to the next node $\pi_{k+1}$;
